\selectlanguage{english}
\chapter{Acknowledgments}

It's with a mix of relief, deep gratitude, and a touch of nostalgia that I now find myself bringing this manuscript to a close with these few words.

First and foremost, I want to thank you, Mohamed. Thank you for being the kind of thesis advisor you were throughout this entire journey: from the early days of shaping this PhD subject during the 2020 lockdown all the way to the final moments of my defense. I truly couldn't have asked for better guidance over these past few years by your side. Thank you for always making yourself available, for helping structure my research, synthesize ideas, and review our papers. Thank you for your encouragement during moments of doubt, when things weren't going smoothly in our work. Thank you for having guided me toward a genuine scientific rigor and mindset. 

I also want to express my gratitude to everyone at the LVML lab at CEA List. Over the years, I've had the chance to cross paths with so many of you —whether over a coffee, on a project, or during a passionate conversation— and I'm thankful for each of those moments.

A big thank you as well to Meero, for giving me the opportunity to complete this thesis under such great conditions. I know how lucky I've been. A special shoutout to everyone on the R\&D team I had the pleasure of meeting along the way. And an especially heartfelt thank you to you, Asya. Thank you for all our passionate discussions, those long debugging sessions, the proofreading, the anxious waiting for some paper notification results, but alsothe joy and the laughs. You made this thesis journey lighter. 

Alexandra, you are —and always will be— the most beautiful encounter I had at Meero. Those few lines will never fit the million reasons I have to thank you, but please know that the \textit{thank you} that follows carries, from the bottom of my heart, all my gratitude. Thank you for everything. You are the most wonderful friend I could ever hope for.

And finally, I want to end these acknowledgments with my parents and my sister. Thank you for your unconditional support, not only throughout this thesis, but far beyond as well. Thank you for always, always being there for me. This thesis wouldn't exist without the infinite love you've given me. I love you.